Python as a machine learning language: experiences from the scikit-learn project

### 2013-06-13 paper.tex
wordings in section 3

\texttt{Pipeline} objects are used for chaining multiple estimators into a
single one. This is useful since a machine learning workflow typically involves
a fixed sequence of steps in processing data (e.g., feature extraction,
normalization, feature selection, learning and making predictions). A sequence
of $N$ such steps can be combined into a composite object called a
\texttt{Pipeline}. The first $N-1$ steps must be transformers and the last can
be either a predictor or a transformer. Conceptually, fitting a pipeline to a
training set amounts to the following recursive procedure: i) when only one step
remains, call its \texttt{fit} method; ii) otherwise, fit the first step, use it
to \texttt{transform} the training set and fit the rest of the pipeline with the
transformed data.
The pipeline exposes all the methods the last
estimator in the pipe exposes. That is, if the last estimator is a predictor,
the pipeline can itself be used as a predictor. If the last estimator is a
transformer, then the pipeline is itself a transformer. \textcolor{red}{TODO:
Talk about nested attribute syntax.}

@@

As the above snippet shows, \texttt{Pipeline} and \texttt{FeatureUnion} can be
combined to create complex objects. In particular, since both are themselves
estimators, they can be used to form nested workflows. \textcolor{red}{TODO:
elaborate a bit more on nested constructions.}

@@

\textcolor{red}{TODO: rewrite and briefly describe the API (see user guide)}\\
\textcolor{red}{TODO: describe Scorer API?}\\
\textcolor{red}{TODO: mention that GridSearchCV objects are themselves estimators}

>>>>

\texttt{Pipeline} objects are used for chaining multiple estimators into a
single one. This is useful since a machine learning workflow typically involves
a fixed sequence of steps in processing data (e.g., feature extraction,
normalization, feature selection, learning and making predictions). A sequence
of $N$ such steps can be combined into a composite object called a
\texttt{Pipeline}. The first $N-1$ steps must be transformers and the last can
be either a predictor or a transformer. Conceptually, fitting a pipeline to a
training set amounts to the following recursive procedure: i) when only one step
remains, call its \texttt{fit} method; ii) otherwise, \texttt{fit} the first
step, use it to \texttt{transform} the training set and \texttt{fit} the rest of
the pipeline with the transformed data. The pipeline exposes all the methods the
last estimator in the pipe exposes. That is, if the last estimator is a
predictor, the pipeline can itself be used as a predictor. If the last estimator
is a transformer, then the pipeline is itself a transformer.

@@

As the above snippet shows, \texttt{Pipeline} and \texttt{FeatureUnion} can be
combined to create complex objects. In particular, since both are themselves
estimators, they can be used to form nested workflows.

@@

\textcolor{red}{TODO: rewrite and briefly describe the API (see user guide)}\\
\textcolor{red}{TODO: describe Scorer API?}\\
\textcolor{red}{TODO: mention that GridSearchCV objects are themselves estimators}
\textcolor{red}{TODO: Talk about nested attribute syntax.}
